---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# outstable

<!-- badges: start -->
<!-- badges: end -->

The goal of `outstable` is to provide a framework for detecting anomalies in tidy time series data. An anomaly is defined  as an observation that is predicted as very unlikely given the robust time series forecast models. The algorithm works with tidy temporal data provided by the [`tsibble`](https://tsibble.tidyverts.org/) package and  produces an outstable, a tsibble with flagged anomalies and their degree of outlierness. An approach based on extreme value theory is applied to residual series in order to calculate a data-driven anomalous threshold. The proposed framework can also provide a cleansed tsibble that closely integrates with the tidy forecasting workflow used in the [`fable`](https://fable.tidyverts.org/) package. A number of different approaches are available for the data cleansing process.

## Installation

<!--
You can install the released version of outstable from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("outstable")
```
-->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pridiltal/outstable")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(outstable)
## basic example code
```
